{\it Maxwell's Silver Hammer:}\\ On pulsed microwave acoustic resonant viral inactivation

### 2021-02-03 documents/brillouin_pulse_math.tex
gosh darnit
Writing!

\begin{itemize}
	\item The highly dispersive nature of tissue, which causes a peculiar distortion of pulses with broadband spectral content,
	\item The variation in loss (the imaginary part of the complex permittivity and the penetration depth) versus frequency. 
\end{itemize}

@@

\subsubsection{Zhu et al 's dispersive waveform optimization propagation formulation}

@@

The Euler-Lagrange equation is usually brought up in the case of the Brachistochrone problem, or 
the Principle of Least Action \footnote{For background, see The Feynman Lectures, vol II chapter 19}. In these types of problems, it appears that the path of integration through space from endpoints a to b can be replaced with the whole frequency domain from -$\infty$ to +$\infty$.

@@

@@

>>>>

\begin{itemize}
	\item The highly dispersive nature of tissue, which causes a peculiar distortion of pulses with broadband spectral content,
	\item The variation in loss (the imaginary part of the complex permittivity and the penetration depth) versus frequency. \wikinote{add image from that mathematica code}
\end{itemize}

@@

\subsubsection{Attempt at analytical solution: Zhu et al 's dispersive waveform optimization propagation formulation}

@@

A common setup for such a problem is to use the Euler-Lagrange equation; this is usually brought up in the case of the Brachistochrone problem, or the Principle of Least Action \footnote{For background, see The Feynman Lectures, vol II chapter 19}. In these types of problems, it appears that the path of integration through space from endpoints a to b is instead replaced by the whole frequency domain from -$\infty$ to +$\infty$.

@@

\ghfile{electronics/propagation/propagation_numerical_optimize.py}

@@

\section{Pulse shaping}

Arbitrary pulses can be formed by

### 2021-02-03 documents/detection.tex
I keep re-writing things but they don't get any better!
Writing!

@@

The plaque assay for viruses has remained essentially unchanged since Delbruck's era.

Advantages over broth methods are the longer infective period without agitation or

@@

@@

@@

>>>>

Two

T4r+,

@@

The plaque assay for viruses has remained essentially unchanged since d'Herelle and Delbruck's era.

Advantages over broth methods are the apparently longer infective period without agitation or

@@

\subsubsection{Protocol and observations}

\begin{toolchain}

To simplify and for higher throughput we use the drop-cast absorption protocol of \cite{Simple2018}, which uses only a single layer of 1\% agar.

150 mL water in a 250 mL beaker covered with alu foil, with stirring, and boiled in a pot of water. 1.5 grams of nutrient agar powder \footnote{Seaweed Inc, Amazon} was added to 150  until molten. A magnetic stir bar was used to ensure all was fully melted,
and then the beaker was autoclaved for 15 minutes. After cooling to 60 C for 25 minutes in a water bath on a hotplate, 20 mL of agar was poured onto [100 mm?] polystyrene plates. The plates were left to set, then dried inverted with a flamed bent copper wire spacer for air exchange at 70 C for [1 hours?].
The plates were then stored inverted in plastic bags at 4 C until use.
\footnote{How agar percentages are specified seems somewhat ambiguous to me - is the percent of the agar itself (a viscosity measure), or the nutrient-agar mix (a growth measure)?
	Weight/weight? It appears to be w/v of the whole dry powder in distilled water.}

After cooling, 1 mL of overnight culture was poured across the plate, excess drained onto the next plate, and allowed to dry for 35 minutes at room temperature.

A control plate was made with pure stock phage and autoclaved phage.

The sample was retrieved from the cuvette by carefully removing the tape backing and withdrawing 0.8 uL from the reverse side, to avoid a silicone oil bubble.

Unfortunately, this ended up being very inconsistent.

Not having a 10 uL pipette, the 0.8 uL sample of phage was diluted in 7.5 uL of sterile broth in a microplate, then all 7.5 uL was added in 2.5 uL steps to the agar.

\st{Each 0.8 uL sample was diluted in 0.2 mL of nutrient broth, a 250x dilution. If the $10^6$ pfu.}

60c to pour was I think too high - condensation was high, even after 1 hour at 37c no change.

". The dryness of the agar is very important; if too moist, the
drops will run and coalesce, if too dry, the bacteria will grow
poorly"

The plates were dried at ~70 C in an oven with the slightly open.

The plates were incubated overnight. The lawn was very nicely formed; the phage concentration was

It was difficult to tell where the drops were placed, and they ran together.

\begin{figure}[H]
	\captionsetup{singlelinecheck = false, justification=justified}
	\centering
	\includegraphics[width=\textwidth]{plaque_assay}
\end{figure}

\end{toolchain}

@@

\subsubsection{Impedance assay}

Because it would be difficult to maintain temperature on and multiplexing was difficult, low-frequency E. coli culture monitoring impedance spectra were performed separately.

An ultra-simple KHz impedance spectrometer was built, following \cite{unconventional2015}.

Purely contactless, capacitively coupled impedance measurement was found to have an unworkably small signal level;
however, a single conduction path and a single capacitive coupling through the Kapton film yielded a 10 mV signal level with 5V Vpp drive. A 110x amplifier was used to bring levels up.

0.7 mm gold-plated spring pins ('pogo' pins) pierced the silicone oil layer and pressed against the bottom tape; 1.4 mm pads were the second electrode.\footnote{Platinum, gold wire, anodized aluminum, or graphite would likely have worked equally well.} The pins were wiped with 99\% alcohol before each test.

2.5 uL stationary e. coli culture was added to 5 uL broth and 2.5 uL phage or autoclaved phage.

0 - 3 were phage; 4-7 were autoclaved phage.

Failure. decrease in signal rather than the expected increase, and no difference between autoclaved and phage.

Looking at this later - the fluid has leaked out of the wells after some time. That might be why this didn't work.

\section{E. coli flavin autofluorescence}

Added 2.5 uL to 5 uL broth. There does seem to be an fluorescence signal from; 100 uS long pulse, -70 mV is a good threshold.
Hz w/e.c, 2.9-5 Hz broth

Put the original eppendorf culture full of e. coli in. Jumped to 18 Hz @ -81 mV! Fantastic!

Thought I was all clever-like, using the oscope trigger out as the comparator and plugging that into a counter,
but above 20 Hz there's no thingy.

No. No go.

Weird background noise.

" By moving into this hydrophobic environment and away from the solvent, the ethidium cation is forced to shed any water molecules that were associated with it. As water is a highly efficient fluorescence quencher, the removal of these water molecules allows the ethidium to fluoresce.[citation needed]"

@@

\subsubsection{Nucleic acid UV extinction }

The 260 nm extinction due to 60 MDa DNA at concentration $10^8 = 10e-9$. With a 1 mm path length is 0.002x. that's going to be swamped by everything else.
